### 2013-01-16 paper_sean/results.tex
s

The simulator enabled HyperNEAT to evolve
fast, organic gaits. In simulation, HyperNEAT gaits were significantly faster than those from Glette et al. (\figref{threeplots}-Top, $\emph{p} < 6.8\times10^{-8}$, comparing the best gaits in the final generation of each run via MATLAB's Wilcoxon rank sum test).  
Specifically, HyperNEAT gaits were 52.1\% faster in simulation (25.4
cm/s, $\pm$ 3.4 SD versus 16.7 cm/s $\pm$ 1.9 SD, \tabref{results} -- qualitative conclusions remain the same even if the analysis is conducted using medians, but to make it easier for comparisons with earlier works~\cite{glette}, we use means $\pm$ SD).
Plots of servo positions over time reveal that the evolved HyperNEAT gaits are regular, smooth and coordinated~(\figref{threeplots}-Left), confirming previous results with HyperNEAT in simulation~\cite{clune2011performance,clune2009evolving}.

>>>>

The simulator enabled HyperNEAT to evolve
fast, organic gaits. In simulation, HyperNEAT gaits were significantly faster than those from Glette et al. (\figref{threeplots}-Top, $\emph{p} < 6.8\times10^{-8}$, comparing the best gaits in the final generation of each run via MATLAB's one-sided Wilcoxon rank sum test).  
Specifically, HyperNEAT gaits were 52.1\% faster in simulation (25.4
cm/s, $\pm$ 3.4 SD versus 16.7 cm/s $\pm$ 1.9 SD, \tabref{results} -- qualitative conclusions remain the same even if the analysis is conducted using medians, but to make it easier for comparisons with earlier works~\cite{glette}, we use means $\pm$ SD).
Plots of servo positions over time reveal that the evolved HyperNEAT gaits are regular, smooth and coordinated~(\figref{threeplots}-Left), confirming previous results with HyperNEAT in simulation~\cite{clune2011performance,clune2009evolving}.
